---
title: "PSTAT 176/276 Project"
output: pdf
author: "William Li, Jiayue Chen, Parsa Hafezi"
---

Executive Summary:



```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyr)
library(tidyverse)
library(readr)
library(PortfolioAnalytics)
library(ROI)
library(ROI.plugin.quadprog)
library(ROI.plugin.glpk)
library(TTR)
library(quantmod)
library(PerformanceAnalytics)
library(quantmod)
library(tidyquant)
library(xts) 
library(ggplot2)
library(highcharter)
library(purrr)
library(dplyr)
library(fredr)
library(FSA)
library(fPortfolio)
library(corpcor)
library(rvest)
library(quadprog)  
library(robust)
library(fields)
library(NMOF)
```
```{r, echo = FALSE}

#Note that we needed to correct to extract monthly
#Step 1 of 16. Note we were asked to extract for the year so that's why I did it this way
#API Key = 75711c32cc2177d3a651e1cef5d26d6a
fredr_set_key("75711c32cc2177d3a651e1cef5d26d6a")

# Consumer Price Index for All Urban Consumers: All Items in U.S. City Average (CPIAUCSL)	
start_date = "2015-01-01"
end_date = "2020-12-31"
CPIAUCSL <- fredr(
  series_id = "CPIAUCSL",
  observation_start = as.Date(start_date),
  observation_end = as.Date(end_date),
  frequency = "m"
)
cpi = subset(CPIAUCSL , select = c(value, date))
ts_cpi_all = as.xts(cpi)
```
```{r, echo = FALSE}
#expense ratios
get_etf_data <- function(ticker) {
  # construct the url for the ETF page on etfdb.com
  url <- paste0("https://etfdb.com/etf/", ticker, "/#etf-ticker-profile")

  # scrape the expense ratio and AUM from the page
  page <- read_html(url)
  expense_ratio <- page %>%
    html_node("div#overview div:nth-child(4) div:nth-child(2)") %>%
    html_text() %>%
    trimws() 
  
  split_string <- strsplit(expense_ratio, "(?<=Largest \\(AUM\\))\\s+", perl = TRUE)[[1]]
  result <- strsplit(split_string[2], "\\s+\\$", perl = TRUE)[[1]]
  ans <- strsplit(result[1], "\\s+", perl = TRUE)[[1]]
  ans <- strsplit(ans[2], "\\%", perl = TRUE)[[1]]
  return(as.numeric(ans[1])/100)
}

```
```{R, echo = FALSE}
#adjust returns
adjust_returns <- function(rets, fees) {
  adj_rets <- rets - fees
  return(adj_rets)
}
```
```{r, echo = FALSE, include = FALSE}
#Step 2/16- set returns for the portfolio
start_date = "2014-12-01" #modify to deal with NAs
end_date = "2020-12-31"
CPIAUCSL <- fredr(
  series_id = "CPIAUCSL",
  observation_start = as.Date(start_date),
  observation_end = as.Date(end_date),
  frequency = "m"
)
cpi = subset(CPIAUCSL , select = c(value, date))
ts_cpi_all = as.xts(cpi)

# Inflation rate
ts_inflation <- na.omit(diff(log(ts_cpi_all))) #same as Return.calculate(ts_cpi_all, method = "log")

# Basis point spread target objective returns for each month
bp_spread_lr <- 0
bp_spread_med <- 100
bp_spread_hi <- 400 #Set some arbitrary value greater than 300 that is reasonable

# Target returns
ts_lr_returns <- ts_inflation + (bp_spread_lr/10000)
ts_med_returns <- ts_inflation + (bp_spread_med/10000)
ts_hi_returns <- ts_inflation + (bp_spread_hi/10000)
head(ts_lr_returns)
```
```{r, echo = FALSE, include = FALSE}
# Step 3 & 4:Daily Returns
start_date = "2014-07-03"  #to deal with nas in rolling returns. 
# Can just select the first point out if you only want 2015-01-01 as start.
end_date = "2020-12-31"
temp <- getSymbols("DIA", src = "yahoo",from = start_date,to = end_date,auto.assign = TRUE) 
temp <- getSymbols("ULST", src = "yahoo",from = start_date,to = end_date,auto.assign = TRUE)
temp <- getSymbols("SPY", src = "yahoo",from = start_date,to = end_date, auto.assign = TRUE) 
DIA_all <- DIA$DIA.Close
ULST_all <- ULST$ULST.Close
SPY_all <- SPY$SPY.Close
DIA_all <- as.xts(DIA_all)
ULST_all <- as.xts(ULST_all)
SPY_all <- as.xts(SPY_all)
head(DIA_all)
```
```{R, echo = FALSE, include = FALSE}
#step 5: daily log returns
rt_SPY_close_daily <- Return.calculate(SPY_all, method = "log")
rt_DIA_close_daily <- Return.calculate(DIA_all, method = "log")
rt_ULST_close_daily <- Return.calculate(ULST_all, method = "log")
n <- nrow(rt_ULST_close_daily)

#adjust for time, keep the other part around for next step
rt_SPY_close_daily_time <- rt_SPY_close_daily[127:(n),]
rt_DIA_close_daily_time <- rt_DIA_close_daily[127:(n),]
rt_ULST_close_daily_time <- rt_ULST_close_daily[127:(n),]
head(rt_SPY_close_daily_time)
head(rt_DIA_close_daily_time)
head(rt_ULST_close_daily_time)
tail(rt_SPY_close_daily_time)
tail(rt_DIA_close_daily_time)
tail(rt_ULST_close_daily_time)
```
```{r, echo = FALSE}
SPYfee <- get_etf_data("SPY")
ULSTfee <- get_etf_data("ULST")
DIAfee <- get_etf_data("DIA")
rt_adj_SPY_close_daily_time <- adjust_returns(rt_SPY_close_daily_time, SPYfee)
rt_adj_DIA_close_daily_time <- adjust_returns(rt_DIA_close_daily_time, DIAfee)
rt_adj_ULST_close_daily_time <- adjust_returns(rt_ULST_close_daily_time, ULSTfee)
```
```{R, echo = FALSE, include = FALSE}
#step 6: drawdown concern/constraint- std. dev
sd_window <- 126 # 6 months of trading days
sd_daily_SPY <- na.omit(rollapply(rt_SPY_close_daily, width = sd_window, FUN = sd, align = "right", fill = NA))
sd_daily_DIA <- na.omit(rollapply(rt_DIA_close_daily, width = sd_window, FUN = sd, align = "right", fill = NA))
sd_daily_ULST <- na.omit(rollapply(rt_ULST_close_daily, width = sd_window, FUN = sd, align = "right", fill = NA))
Tolerable_stdDev <- -8* sd_daily_SPY #note we can't have a loss that drops below the given limit on a single day
Tolerable_stdDev
```

First, we will note our asset selection for our low-risk portfolio. We will not apply asset rotations since this portfolio is not trying to chase yield. The two key components of a low risk portfolio that beats out CPI, or inflation, is considered to be bond heavy. Since Vanguards "BIV" ETF has the lowest fee (up to this year) through a little known patent, I chose it. Note this is an investment into medium term bonds only, so to deal with that risk we will consider short term bonds through the "BSV", or Vanguard's short term bond index as well. We will additionally consider Berkshire Hathaway as an investment, as it provides a diversified set of companies in the case the fixed income market declines, as typically when bonds go down equities go up, as well as the S&P 500 through "VOO" since "VOO" has a lower fee than SPY. Note the previous statement has not been true as of 2022, since there has been a historic change in the valuation of the dollar. 
Lastly, we will increase our asset allocation in key areas of gold, technology, and general consumer appliances. This can be done through "GLD", the SPDR gold ETF, for precious metals allocation. We will also consider Cadence("CDNS") for EDA and General Electric ("GE") for legacy technologies, as well as Google ("GOOD") for cloud computing & utility. We will further consider General Mills ("GIS") and Walmart ("WMT") because people like food and low cost goods, and there two are major brands in that area.  
We will further consider the cost of fertilizer through CF Industries Holdings, since the price of fertilizer is a major factor in the price of food ("CF").


```{R, echo = FALSE, include = FALSE}
#Step 7: read daily CLOSE prices for all assets
tickers = c("BIV", "BSV", "VOO", "GLD", "BRK-B", "CDNS", "GE", "GOOG", "GIS", "WMT", "CF", "V", "JPM", "AMZN", "MSFT", "JNJ", "PG")
```
```{r, echo = FALSE, include = FALSE}
# Expense Ratios:
BIVfee <- get_etf_data("BIV")
BSVfee <- get_etf_data("BSV")
Voofee <- get_etf_data("VOO")
GLDfee <- get_etf_data("GLD")
fees <- c(BIVfee, BSVfee, Voofee,GLDfee)
for (i in seq(length(tickers) - 4)){
  fees <- c(fees, 0)
}
fees
```
```{r, echo = FALSE, include = FALSE}
#8: Daily Returns: Close only
start_date = "2014-04-03"
pr_daily <- getSymbols(tickers, src = "yahoo",
           from = start_date,
           to = end_date,
           auto.assign = TRUE) %>% 
  map(~Cl(get(.))) %>% 
  reduce(merge)
pr_daily = as.xts(pr_daily)
rt_daily <- na.omit(Return.calculate(pr_daily, method = "log"))
fee_adj_rt_daily <- adjust_returns(rt_daily, fees)
fee_adj_rt_daily 
```

Here we graph the efficient frontier for 6 months of historical covariance. This particular efficient frontier is computed to show the distribution of assets at 2015-01-02.
```{r, echo = FALSE}
# Parts 9, 10, 11: Choose historical window of 6 months.
# Calculate assets-log returns at each rebalance date, & construct covariance matrix at each rebalance date (1st of each month)
# Set the window size to 126 trading days
window_size <- 126
# Calculate the 6-month rolling log returns
rolling_returns_6month <- rollapply(fee_adj_rt_daily, width = window_size, FUN = function(x) sum(x), align = "right", fill = NA) #since logarithms are additive
# Remove rows with missing values
rolling_returns_6month <- na.omit(rolling_returns_6month)
                                  
# Get the indices of the first observation of each month
month_endpoints <- endpoints(rolling_returns_6month, on = "months") + 1
month_endpoints <- month_endpoints[1:(length(month_endpoints)-1)]
# Subset the rolling_returns_6month object using the indices of the first observation of each month
rolling_returns_6month_monthly <- rolling_returns_6month[month_endpoints]
new_start_date = "2015-01-01"
fee_adj_rt_monthly <- window(rolling_returns_6month_monthly, start = new_start_date)
#fee_adj_rt_monthly <- window(rolling_returns_6month, start = new_start_date)
```

```{r, echo = FALSE}
#calculate cov matrix for 2015-01-02
new_start_date = "2015-01-02"  # Changing this changes the cov matrix & frontier
fee_adj_rt_monthly <- window(rolling_returns_6month_monthly, start = new_start_date)

sampCovRobMCD <- covRob(fee_adj_rt_monthly, estim = "mcd", quan = 0.95, ntrial = 10000)
mu <- sampCovRobMCD$center
varcov <- sampCovRobMCD$cov

# Heatmap of the estimated variance-covariance matrix
layout(matrix(c(1, 2), nrow = 1, byrow = TRUE), widths = c(4, 1))
# Create the heatmap
heatmap(varcov, Rowv = NA, Colv = NA, col = colorRampPalette(c("blue", "white", "red"))(25))
# Create the legend
image.plot(legend.only = TRUE, col = colorRampPalette(c("blue", "white", "red"))(25), zlim = range(varcov))
# Number of assets
nvar <- length(mu)

# Number of efficient frontier points
n.er <- 100  
rset <- seq(min(mu), max(mu), length=n.er+2)
rset <- rset[2:n.er+1]

# Initialize variables to store results
port.ret <- rset
port.std <- rset*0
port.wgt <- matrix(0, n.er, nvar)

# Calculate efficient frontier using quadratic programming
for (i in 1:(n.er-1)) {
  Dmat <- 2*varcov
  dvec <- rep(0, nvar) 
  Amat <- t(rbind(t(rep(1, nvar)), t(mu), diag(nvar)))
  bvec <- c(1, rset[i], rep(0, nvar))
  
  # Mean-variance optimization
  m <- solve.QP(Dmat, dvec, Amat, bvec, meq = 2)
  
  # Store results
  port.std[i]  <- sqrt(m$value)
  port.wgt[i,] <- t(m$solution)
}

# Efficient frontier 
plot(sqrt(diag(varcov)), mu, xlim=c(0.8*min(port.std),1.6*max(port.std)), 
     ylim=c(1.2*min(mu), 1.2*max(mu)), col = rainbow(nvar), lwd = 10, 
     xlab = expression(sigma), ylab = expression(mu))
text(sqrt(diag(varcov)), mu, labels = tickers, cex= 1)
lines(port.std, port.ret, col = "black", lwd = 1)
```
```{r, echo = FALSE, include = FALSE} 
# Now, we need to calculate MCD for all covariance matrices, not just time 01-02-2015!

dim(fee_adj_rt_monthly) #is 72 x 11
dim(varcov) #produces 11 x 11 covariance matrix at each time point.
```


```{r, echo = FALSE}
# Set the start and end dates
start_date <- as.Date("2015-01-01")
end_date <- as.Date("2020-12-01")

# Set the window size to 126 trading days
window_size <- 126

# Calculate the 6-month rolling returns at a daily time scale
rolling_returns_6month <- rollapply(fee_adj_rt_daily, width = window_size, FUN = function(x) sum(x), align = "right", fill = NA)

# Remove rows with missing values
rolling_returns_6month <- na.omit(rolling_returns_6month)
rolling_returns_6month_1 <- window(rolling_returns_6month, start = start_date)                           
# Get the indices of the first observation of each month
month_endpoints <- endpoints(rolling_returns_6month_1, on = "quarters") + 1
month_endpoints <- month_endpoints[1:(length(month_endpoints)-1)]
# Subset the rolling_returns_6month object using the indices of the first observation of each month
#rolling_returns_6month_monthly <- rolling_returns_6month[month_endpoints]

# Initialize a list to store the variance-covariance matrices
mu_list <- list()
varcov_list <- list()


current_date <- index(rolling_returns_6month_1[month_endpoints[2]])
current_date 

fee_adj_rt_monthly <- window(rolling_returns_6month_1, start = current_date)
  
# Calculate the variance-covariance matrix
sampCovRobMCD <- covRob(fee_adj_rt_monthly, estim = "mcd", quan = 0.95, ntrial = 10000)
sampCovRobMCD
```

```{r, echo = FALSE}
# Loop through each time period. Computes
for (i in 1:60) {
  
  # Get the returns for the current time period
  current_date <- index(rolling_returns_6month_1[month_endpoints[i]])
  fee_adj_rt_monthly <- window(rolling_returns_6month_1, start = current_date)
  
  # Calculate the variance-covariance matrix
  sampCovRobMCD <- covRob(fee_adj_rt_monthly, estim = "mcd", quan = 0.95, ntrial = 10000)
  mu_list[[i]] <- sampCovRobMCD$center
  varcov_list[[i]] <- sampCovRobMCD$cov
  
}

# Convert the list to a 3D array
varcov_array <- array(unlist(varcov_list), dim = c(nrow(fee_adj_rt_monthly), ncol(fee_adj_rt_monthly), length(varcov_list)))

# Check the dimensions of the array
dim(varcov_array)
```



```{r}
library(gridExtra)

# Define start and end dates
start_date <- as.Date("2014-12-31")
end_date <- as.Date("2020-12-31")

# Define number of quarters
nquarters <- as.numeric(as.yearqtr(end_date) - as.yearqtr(start_date)) * 4

# Initialize list to store plots
plots <- vector("list", nquarters)

# Loop over each quarter
for (i in seq_len(nquarters)) {
  # Calculate start and end dates for current quarter
  new_start_date <- as.Date(as.yearqtr(start_date) + (i-1)/4)
  new_end_date <- as.Date(as.yearqtr(start_date) + i/4 - 1/365)
  
  # Calculate covariance matrix and efficient frontier for current quarter
  #fee_adj_rt_monthly <- window(rolling_returns_6month_monthly, start = new_start_date)
  #sampCovRobMCD <- covRob(fee_adj_rt_monthly, estim = "mcd", quan = 0.95, ntrial = 10000)
  current_date <- index(rolling_returns_6month_1[month_endpoints[i]])
  fee_adj_rt_monthly <- window(rolling_returns_6month_1, start = current_date)
  
  # Calculate the variance-covariance matrix
  sampCovRobMCD <- covRob(fee_adj_rt_monthly, estim = "mcd", quan = 0.95, ntrial = 10000)
  
  
  mu <- sampCovRobMCD$center
  varcov <- sampCovRobMCD$cov
  nvar <- length(mu)
  n.er <- 100  
  rset <- seq(min(mu), max(mu), length=n.er+2)
  rset <- rset[2:n.er+1]
  port.ret <- rset
  port.std <- rset*0
  port.wgt <- matrix(0, n.er, nvar)
  for (j in 1:(n.er-1)) {
    Dmat <- 2*varcov
    dvec <- rep(0, nvar) 
    Amat <- t(rbind(t(rep(1, nvar)), t(mu), diag(nvar)))
    bvec <- c(1, rset[j], rep(0, nvar))
    m <- solve.QP(Dmat, dvec, Amat, bvec, meq = 2)
    port.std[j]  <- sqrt(m$value)
    port.wgt[j,] <- t(m$solution)
  }
  
  # Store plot in list
  plots[[i]] <- plot(sqrt(diag(varcov)), mu, xlim=c(0.8*min(port.std),1.6*max(port.std)), 
                     ylim=c(1.2*min(mu), 1.2*max(mu)), col = rainbow(nvar), lwd = 10, 
                     xlab = expression(sigma), ylab = expression(mu))
  text(sqrt(diag(varcov)), mu, labels = tickers, cex= 1)
  lines(port.std, port.ret, col = "black", lwd = 1)
}

# Arrange plots in a grid
gridExtra::grid.arrange(grobs = plots)

```









```{r, echo = FALSE}
CPIAUCSL <- fredr(
  series_id = "CPIAUCSL",
  observation_start = as.Date("2014-12-01"),
  observation_end = as.Date("2020-12-31")
)

# Make it into an xts file
CPIAUCSL <- xts(CPIAUCSL$value, order.by = CPIAUCSL$date)

# Storing CPIAUCSL data
write.zoo(CPIAUCSL, file="CPIAUCSL.csv", sep=",")
```
```{r, echo = FALSE}
CPIAUCSL <- xts(read.zoo("CPIAUCSL.csv", sep =","))
```
```{r, echo = FALSE}
# Monthly inflation rate  
rt_CPIAUCSL <- na.omit(Return.calculate(CPIAUCSL, method = "log"))

# Target monthly portfolio returns across risk profiles
options(scipen = 999)
rt_target <- merge.xts(rt_CPIAUCSL+0.03, rt_CPIAUCSL+0.01, rt_CPIAUCSL)
colnames(rt_target) <- c("Profile 1", "Profile 2", "Profile 3")
head(rt_target)

ben_symbols <- c("SPY", "DIA", "ULST")
# Obtaining benchmark data
start_date <- "2014-12-31"
end_date <- "2020-12-31"
df_Assets <- getSymbols(ben_symbols, from = start_date, to = end_date)

# Storing the benchmark prices in one array
prices_ben <- purrr::map(ben_symbols, function(x) Ad(get(x)))
prices_ben <- purrr::reduce(prices_ben, merge)
colnames(prices_ben) <- ben_symbols

# Computing daily returns
rt_ben <- na.omit(Return.calculate(prices_ben, method = "log"))

# Target average daily return across risk profiles adjusted for the rebalancing period
int <- 3
rebal_per <- int
diff_in_months <- (year(ymd(end_date))  - year(ymd(start_date))) * 12 +
                  (month(ymd(end_date)) - month(ymd(start_date)))
rebal_freq <- diff_in_months/rebal_per

start_date_loop <- index(rt_ben[1,0])
for (per in 1:rebal_freq) {
  # Get time period
  end_date_loop <- start_date_loop %m+% months(rebal_per)
  end_date_loop <- end_date_loop - days(lubridate::day(end_date_loop))
  if (per == 1){
    start_date_loop <- start_date_loop - days(lubridate::day(start_date_loop)-1)  
  }
  
  # Select rebalancing period
  rt_rebal_per <- colSums(rt_target[paste0(start_date_loop, "/", end_date_loop)])
  ct_day <- nrow(rt_ben[paste0(start_date_loop, "/", end_date_loop)])
  dates <- index(rt_ben[paste0(start_date_loop, "/", end_date_loop)][,0])
  
  # Compute average target daily return 
  if (per == 1) {
    rt_tgt <- xts(matrix(rep(rt_rebal_per/ct_day, ct_day), nrow = ct_day, ncol = 3, 
                         byrow = T), order.by = dates)
    colnames(rt_tgt) <- c("Profile 1", "Profile 2", "Profile 3")
  } else {
    rt_tgt <- rbind(rt_tgt, xts(matrix(rep(rt_rebal_per/ct_day, ct_day), 
                                    nrow = ct_day, ncol = 3, byrow = T), order.by = dates))
  }

  start_date_loop <- end_date_loop + days(1)
}
head(rt_tgt)
```


```{r, message = FALSE, echo = FALSE} 
start_date <- "2014-12-31"
end_date <- "2020-12-31"
df_Assets <- getSymbols(tickers, from = start_date, to = end_date)

# Storing the prices in one array
prices <- purrr::map(tickers, function(x) Ad(get(x)))
prices <- purrr::reduce(prices, merge)
colnames(prices) <- tickers

# Computing daily returns
rt_daily <- na.omit(Return.calculate(prices, method = "log"))
rt_daily <- adjust_returns(rt_daily, fees)
```
Rebal freq needs to be an integer!
```{r, message = FALSE, echo = FALSE} 
# Need to include Risk profiles 3
set.seed(1)

# Number of assets
nvar <- length(tickers)

# Rebalancing period in months
rebal_per <- int
diff_in_months <- (year(ymd(end_date))  - year(ymd(start_date))) * 12 +
                  (month(ymd(end_date)) - month(ymd(start_date)))
rebal_freq <- diff_in_months/rebal_per
```
```{r, echo = FALSE}
# Decrease the start date date by 3 months
prev_date <- ymd(start_date) %m-% months(rebal_per)

# Obtaining stock data for the first portfolio weights
df_Assets_init <- getSymbols(tickers, from = prev_date, to = start_date)
prices_init <- purrr::map(tickers, function(x) Ad(get(x)))
prices_init <- purrr::reduce(prices_init, merge)
colnames(prices_init) <- tickers
rt_daily_init <- na.omit(Return.calculate(prices_init, method = "log"))

# Initializing portfolio weights
port.wts <- matrix(0, rebal_freq, nvar)
portRisk3.wts <- matrix(0, rebal_freq, nvar)
portGMV.wts <- matrix(0, rebal_freq, nvar)

# Computing the robust variance-covariance matrix
sampCovRobMCD_init <- covRob(rt_daily_init, estim = "mcd", quan = .95, ntrial = 10000)
mu_init <- sampCovRobMCD_init$center
varcov_init <- sampCovRobMCD_init$cov

# Specific target risk
#if (FALSE) {
  # Pick risk profile 3
  tgt_pro_3 <- as.numeric(rt_tgt[index(rt_daily[1,]), 3])

  # Efficient portfolio with target return for risk profile 3
  efficient_portfolio <- tseries::portfolio.optim(x = rt_daily_init, pm = tgt_pro_3, 
                            covmat = varcov_init, reshigh = rep(1.2, nvar), 
                            reslow = rep(-0.2, nvar), riskless = FALSE, shorts=TRUE)
  portRisk3.wts[1,] <- efficient_portfolio$pw
#}

# Minimum variance portfolio
#if (FALSE) {
  # This is a multiline comment block.
  # The code inside this block will not be executed.
  Sigma <- varcov_init
  ones <- rep(1, ncol(Sigma)) # vector of ones
  invSigma <- solve(Sigma) # inverse of covariance matrix

  # Calculate weights for minimum variance portfolio
  portGMV.wts[1,] <- t(invSigma %*% ones / sum(invSigma %*% ones))
#}

# Max Sharpe Portfolio with box constraints
port.wts[1,] <- maxSharpe(m = as.numeric(mu_init), var = matrix(varcov_init, ncol = nvar), 
                          wmin = -0.2, wmax = 1.2)

start_date_loop <- index(rt_daily[1,0])
for (rper in 2:rebal_freq) {
  end_date_loop <- start_date_loop %m+% months(rebal_per)
  
  # Correct for day differences
  end_date_loop <- end_date_loop - days(lubridate::day(end_date_loop))
  window_returns <- rt_daily[paste0(start_date_loop, "/", end_date_loop)]
  
  # Computing the robust variance-covariance matrix
  sampCovRobMCD <- covRob(rt_daily, estim = "mcd", quan = .95, ntrial = 10000)
  mu <- sampCovRobMCD$center
  varcov <- sampCovRobMCD$cov
  
  # Specific target risk
  #if (FALSE) {
  # Pick risk profile 3
  # Use a time window of one week to adjust for weekend and other non-trading days 
  tgt_pro_3 <- mean(as.numeric(rt_tgt[paste0(end_date_loop + days(1), "/", 
                                             end_date_loop + days(7)), 3]))

  # Efficient portfolio with target return = mean of returns
  efficient_portfolio <- tseries::portfolio.optim(x = window_returns, pm = tgt_pro_3, 
                                  covmat = varcov, reshigh = rep(1.2, nvar), 
                                  reslow = rep(-0.2, nvar), riskless = FALSE, shorts=TRUE)
  portRisk3.wts[rper,] <- efficient_portfolio$pw
  #}
  
  # Get the minimum variance portfolio
  #if (FALSE) {
    # This is a multiline comment block.
    # The code inside this block will not be executed.
    Sigma <- varcov
    ones <- rep(1, ncol(Sigma)) # vector of ones
    invSigma <- solve(Sigma) # inverse of covariance matrix

    # Calculate weights for minimum variance portfolio
    portGMV.wts[rper,] <- t(invSigma %*% ones / sum(invSigma %*% ones))
  #}
  
  # Max Sharpe Portfolio with box constraints
  port.wts[rper,] <- maxSharpe(m = as.numeric(mu), var = matrix(varcov, ncol = nvar), 
                          wmin = -0.2, wmax = 1.2)

  start_date_loop <- end_date_loop + days(1)
}
par(mfrow = c(1,1), mar = c(3,2,2,3), xpd=TRUE)
barplot(t(port.wts), col=rainbow(nvar), ylab = "Weights", beside = TRUE)
legend("topright", legend = tickers, fill = rainbow(nvar), ncol = 1, inset=c(-0.1,0), cex = 0.8)

par(mfrow = c(1,1), mar = c(3,2,2,3), xpd=TRUE)
barplot(t(portRisk3.wts), col=rainbow(nvar), ylab = "Weights", beside = TRUE)
legend("topright", legend = tickers, fill = rainbow(nvar), ncol = 1, inset=c(-0.1,0), cex = 0.8)

par(mfrow = c(1,1), mar = c(3,2,2,3), xpd=TRUE)
barplot(t(portGMV.wts), col=rainbow(nvar), ylab = "Weights", beside = TRUE)
legend("topright", legend = tickers, fill = rainbow(nvar), ncol = 1, inset=c(-0.1,0), cex = 0.8)
```

```{r, message = FALSE, echo = FALSE} 
# Manually computing portfolio returns
rt_ptf <- rt_daily[,1]
colnames(rt_ptf) <- "portfolio.return"
for (i in 1:nrow(rt_daily)){
  k <- ceiling(month(index(rt_daily[i,0]))/ rebal_per)
  rt_ptf[i,] <- sum(port.wts[k,]*rt_daily[i,])
}
# Manually computing portfolio returns
rt_ptfR3 <- rt_daily[,1]
colnames(rt_ptfR3) <- "portfolio.return"
for (i in 1:nrow(rt_daily)){
  k <- ceiling(month(index(rt_daily[i,0]))/ rebal_per)
  rt_ptfR3[i,] <- sum(portRisk3.wts[k,]*rt_daily[i,])
}

# Manually computing portfolio returns
rt_ptfGMV <- rt_daily[,1]
colnames(rt_ptfGMV) <- "portfolio.return"
for (i in 1:nrow(rt_daily)){
  k <- ceiling(month(index(rt_daily[i,0]))/ rebal_per)
  rt_ptf[i,] <- sum(portGMV.wts[k,]*rt_daily[i,])
}
```

```{r, echo = FALSE}  
# Window of benchmark returns
window <- 6

benchmark <- "SPY"
df_Assets <- getSymbols(benchmark, from = ymd(start_date) %m-% months(window), to = end_date)

# Storing the prices in one array
price_ben <- purrr::map(benchmark, function(x) Ad(get(x)))
price_ben <- purrr::reduce(price_ben, merge)
colnames(price_ben) <- benchmark

# Computing daily benchmark returns
rt_daily_ben <- na.omit(Return.calculate(price_ben, method = "log"))

idx <- which(index(rt_daily_ben[,0]) == index(rt_ptf[1,0]))
win_day <- length(rt_daily_ben)-length(rt_ptf)
```
```{r, echo = FALSE}  
for (i in idx:length(rt_daily_ben)){
  # Standard deviations of the benchmark over the window length 
  threshold <- -8*sd(rt_daily_ben[(i-win_day):i, ])
  if (rt_ptf[(i-win_day),] < threshold){
    print(paste("Breached on", index(rt_ptf[(i-win_day), 0])))
    print(paste((rt_ptf[(i-win_day),])))
    print(paste(threshold))
    break
  }
}
```
```{r, echo = FALSE}  
for (i in idx:length(rt_daily_ben)){
  # Standard deviations of the benchmark over the window length 
  threshold <- -8*sd(rt_daily_ben[(i-win_day):i, ])
  if (rt_ptfR3[(i-win_day),] < threshold){
    print(paste("Breached on", index(rt_ptf[(i-win_day), 0])))
    print(paste((rt_ptf[(i-win_day),])))
    print(paste(threshold))
    break
  }
}
```
```{r, echo = FALSE}  
for (i in idx:length(rt_daily_ben)){
  # Standard deviations of the benchmark over the window length 
  threshold <- -8*sd(rt_daily_ben[(i-win_day):i, ])
  if (rt_ptfGMV[(i-win_day),] < threshold){
    print(paste("Breached on", index(rt_ptf[(i-win_day), 0])))
    print(paste((rt_ptf[(i-win_day),])))
    print(paste(threshold))
    break
  }
}
```


```{r PF-Fee, eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE}
fee_rate <- 0.001

# Portfolio value at the beginning of each rebalancing period
port_val <- rep(0, rebal_freq+1)
port_val[1] <- c(10^7)*(1-fee_rate)

# Matrix of portfolio positions in USD
# at the end of each rebalancing period
positions <- matrix(0, nrow = rebal_freq, ncol = nvar)

# Accumulated fees
fees <- 10^7*fee_rate

start_date_loop <- index(rt_daily[1,0])
for (per in 1:rebal_freq) {
  # Get time period
  end_date_loop <- start_date_loop %m+% months(rebal_per)
  end_date_loop <- end_date_loop - days(lubridate::day(end_date_loop))
  
  # Return per rebalancing period
  x0 <- prices[paste0(start_date_loop, "/", end_date_loop)]
  rt_per <- as.numeric(x0[nrow(x0),])/as.numeric(x0[1,])
  
  # Portfolio value at the end of the rebalancing period
  positions[per,] <- port_val[per]*port.wts[per,]*rt_per
  
  # Perform rebalancing
  dollar <- sum(positions[per,])
  if (per != rebal_freq){
    target <- dollar*port.wts[per+1,]
  } else {
    # Liquidate the entire position at the end and return cash to investors
    target <- rep(0, nvar)
  } 
  
  # Record fees and portfolio value at the beginning of the new period
  fees <- fees + sum(abs(target - positions[per,]))*fee_rate
  port_val[per+1] <- dollar - sum(abs(target - positions[per,]))*fee_rate
  
  start_date_loop <- end_date_loop + days(1)
}

options(scipen = 999)
par(mfrow = c(1,1), mar = c(3,2,2,3), xpd=TRUE)
bp1 <- barplot(t(positions), col=rainbow(nvar), ylim = c(min(positions), max(positions)), ylab = "Weights", beside = T)
legend("topright", legend = tickers, fill = rainbow(nvar), ncol = 1, inset=c(-0.1,0), cex = 0.8)

# Total fees paid
fees

# Plot portfolio value over time
bp <- barplot(port_val[2:(rebal_freq+1)], ylim = c(0, max(port_val)*1.1), xlab = 'Quarter', 
     ylab = 'Dollar Value', main = 'Portfolio Value')
text(bp, round(port_val[2:(rebal_freq+1)], 3), labels = round(port_val[2:(rebal_freq+1)]/10^6,3), pos = 3)
```
```{r}
# Yearly target return of risk profile 2 portfolio 
(rt_yr_tgt <- colSums(rt_tgt[period, ]))
```
```{r}
if (rt_yr_ptf < rt_yr_tgt[1]){
  print(paste("Failed to meet yearly target return of risk profile 1 in", year(period)))
}
if (rt_yr_ptf < rt_yr_tgt[2]){
  print(paste("Failed to meet yearly target return of risk profile 2 in", year(period)))
}
if (rt_yr_ptf < rt_yr_tgt[3]){
  print(paste("Failed to meet yearly target return of risk profile 3 in", year(period)))
}
```
