---
title: "Li-portion"
output: html_notebook
---


```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Load packages
#install.packages("tidyr")
library(tidyr)
#install.packages("tidyverse")
library(tidyverse)
#install.packages("readr")
library(readr)
#install.packages("PortfolioAnalytics")
library(PortfolioAnalytics)
#install.packages("ROI")
library(ROI)
#install.packages("ROI.plugin.quadprog")
library(ROI.plugin.quadprog)
#install.packages("ROI.plugin.glpk")
library(ROI.plugin.glpk)
#install.packages('quantmod')
#install.packages('TTR')
library('TTR')
library('quantmod')

library(PerformanceAnalytics)
library(quantmod)
#install.packages("tidyquant")
library(tidyquant)
library(xts) 
library(ggplot2)
#install.packages("highcharter")
library(highcharter)
library(purrr)
library(dplyr)
#install.packages("fredr")
library(fredr)
#install.packages("FSA")
library(FSA)
library(fPortfolio)
library(corpcor)

start_date = "2015-01-01"
end_date = "2020-12-31"
```


1. Fred Data
```{r}
#API Key = 75711c32cc2177d3a651e1cef5d26d6a
fredr_set_key("75711c32cc2177d3a651e1cef5d26d6a")

# Consumer Price Index for All Urban Consumers: All Items in U.S. City Average (CPIAUCSL)	

CPIAUCSL <- fredr(
  series_id = "CPIAUCSL",
  observation_start = as.Date(start_date),
  observation_end = as.Date(end_date)
)

cpi = subset(CPIAUCSL , select = c(value, date))

ts_cpi = as.xts(cpi)
chart_Series(ts_cpi , name="CPI")
```
"BRK-B": Berkshire Hathaway
"APPL": Apple
"VOO" (.03% fee): SPY with a lower fee
"QCOM": Qualcomm (RF)
"BIV" (.04% fee): Bonds
"WMT": Walmart
"JCPNQ": JC Penny
"CDNS": Cadence
"KEYS": Keysight
"GE": General Electric
"GIS": General Mills
"MS": Morgan Stanley
"GS": Goldman Sachs
"CS": Credit Suisse
"VIXM": VIX midterm futures (varying expense ratio)

Expense Ratios:
```{r, echo = FALSE}
library(rvest)
get_etf_data <- function(ticker) {
  # construct the url for the ETF page on etfdb.com
  url <- paste0("https://etfdb.com/etf/", ticker, "/#etf-ticker-profile")

  # scrape the expense ratio and AUM from the page
  page <- read_html(url)
  expense_ratio <- page %>%
    html_node("div#overview div:nth-child(4) div:nth-child(2)") %>%
    html_text() %>%
    trimws() 
  
  split_string <- strsplit(expense_ratio, "(?<=Largest \\(AUM\\))\\s+", perl = TRUE)[[1]]
  result <- strsplit(split_string[2], "\\s+\\$", perl = TRUE)[[1]]
  ans <- strsplit(result[1], "\\s+", perl = TRUE)[[1]]
  ans <- strsplit(ans[2], "\\%", perl = TRUE)[[1]]
  return(as.numeric(ans[1])/100)
}

```
```{r}
Voofee <- get_etf_data("VOO")
BIVfee <- get_etf_data("BIV")
VIXMfee <- get_etf_data("VIXM")
fees <- c(Voofee,BIVfee, VIXMfee)
for (i in seq(length(tickers) - 3)){
  fees <- c(fees, 0)
}
fees
```

Daily Returns
```{r, echo = FALSE}
tickers = c("VOO", "BIV", "VIXM", "BRK-B", "AAPL", "QCOM", "WMT", "CDNS", "KEYS", "GE", "GIS", "MS", "GS", "CS")

pr_daily <- getSymbols(tickers, src = "yahoo",
           from = start_date,
           to = end_date,
           auto.assign = TRUE) %>% 
  map(~Ad(get(.))) %>% 
  reduce(merge)
```

```{r, echo = FALSE}
pr_daily = as.xts(pr_daily)
head(pr_daily)
```

Daily Log Returns
```{r, echo = FALSE}
rt_daily <- na.omit(Return.calculate(pr_daily, method = "log"))
head(rt_daily)
```


Constrained Portfolio
```{r, echo = FALSE}
# Create Portfolio object which is essentially a list object
low_exp_return_portfolio <- PortfolioAnalytics::portfolio.spec(assets = tickers)

low_exp_return_portfolio <- PortfolioAnalytics::add.constraint(
  portfolio = low_exp_return_portfolio,
  type = "full_investment")
low_exp_return_portfolio <- PortfolioAnalytics::add.constraint(
  portfolio = low_exp_return_portfolio,
  type = "box", min = -0.05, max = .7
)
low_exp_return_portfolio <- PortfolioAnalytics::add.constraint(
  portfolio = low_exp_return_portfolio,
  type = "transaction cost", ptc = .001 #.1% transaction cost
)
low_exp_return_portfolio <- add.constraint(low_exp_return_portfolio, type = "position", 
                       min_sum = 1, max_sum = 1.2)

# Add objective to minimize variance
low_exp_return_portfolio <- PortfolioAnalytics::add.objective(
  portfolio = low_exp_return_portfolio,
  # Minimize risk
  type = "return",
  name = "var"
)

```


Need some function to adjust returns due to fees:
```{R}
adjust_returns <- function(rets, fees) {
  adj_rets <- rets - fees
  return(adj_rets)
}
adj_rt_daily <- adjust_returns(rt_daily, fees)
```


max portfolio
```{r , echo = TRUE}

global_min_portfolio <- PortfolioAnalytics::optimize.portfolio(
  R = adj_rt_daily, #need to replace with some adjusted return function
  portfolio = low_exp_return_portfolio,
  optimize_method = "quadprog",
  # Return additional information on the path or portfolios searched
  trace = TRUE
)
# Examine returned portfolio list object
global_min_portfolio
```


```{r Markowitz 5, echo = TRUE}

# Set optimal weights
weights <- pluck(.x = global_min_portfolio, "weights")
# Check if the weights and symbols align
tibble(weights, tickers)

```

```{r Markowitz 6, echo = TRUE}

# Ensure that the weights vector sums up to 1
tibble(weights, tickers) %>%
  dplyr::summarize(total_weight = sum(weights))


```



```{r Markowitz 8, echo = TRUE}

# Compute monthly portfolio returns
portfolio_returns_xts_rebalanced <-
  PerformanceAnalytics::Return.portfolio(
    R = rt_daily,
    weights = weights,
    # Monthly re-balancing
    reblance_on = "monthly",
    # Use simple/arithmetic chaining to aggregate returns
    geometric = FALSE
  ) %>%
  `colnames<-`("portfolio_returns")
# Examine
head(portfolio_returns_xts_rebalanced, 5)

```
```{r, echo = FALSE}
chart_Series(portfolio_returns_xts_rebalanced , name="Portfolio Returns")
```







```{r, echo = FALSE}
portfolio_returns_xts_rebalanced <-
  PerformanceAnalytics::Return.portfolio(
    R = pr_daily,
    weights = weights,
    # Monthly re-balancing
    reblance_on = "monthly",
    # Use simple/arithmetic chaining to aggregate returns
    geometric = FALSE
  ) %>%
  `colnames<-`("portfolio_returns")
# Examine
head(portfolio_returns_xts_rebalanced, 5)

chart_Series(portfolio_returns_xts_rebalanced , name="Portfolio Returns")
```
